\documentclass[11pt]{article}
\usepackage{enumerate}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{listings}
\pagestyle{empty} \setlength{\parindent}{0mm}
\addtolength{\topmargin}{-0.5in} \setlength{\textheight}{9.5in}
\addtolength{\textwidth}{0.5in} \addtolength{\oddsidemargin}{-0.5in}

\begin{document}

\begin{center}
\textbf{Logan Sims \\ CSCI 402 \\ Homework 1  }
\end{center}

\begin{enumerate}[1.]
\item
$\forall x \: (F^1(x) \:\land\: (\forall y(G^1(y)\: \land\: J^2(x,y)\: \land\: L^4(x,x,x,y)))\: \rightarrow \newline H^2(x,x) \:\land\: \forall y\:(J^2(y,x) \rightarrow \:\lnot\: H^2(y,x)))$ 
\item
$\forall x\: (F^1(x) \:\land\: \lnot\: \exists y\: (H^2(y,x))\: \land\: \lnot\: G^1(x)\: \rightarrow\: \forall y\: (H^2(y,x)\: \rightarrow\: \lnot\: J^2(x,y)))$ 
\item
\textbf{System}\\
M = person telling the story.

father(F, M)\\
married(M, W)\\
daughter(D, W)\\
married(D, F)\\
son(S1, W)\\
son(S2, D)\\
brother-in-law(S1, W)\\
uncle(S1, M)\\
mother(D, M)\\
step-daughter(D, M)\\
son-in-law(F, M)\\
\textbf{Expressions}
\begin{enumerate}[1.]
\item
$daughter(x, y)\land \lnot daughter(x, z) \land married(y, z) \land male(z) \rightarrow step-father(z, x)$
\item
$(father(x, y) \lor step-father(x, y)) \land married (y, z) \rightarrow father-in-law(x, z)$
\item
$(father(x, y) \lor father-in-law(x, y)) \land (father(y, z) \lor father-in-law(y, z)) \rightarrow grandfather(x, z)$
\end{enumerate}
\textbf{Own Grandfather Proof}\\
Using modus ponens on expression 1 with x = D, y = W, and z = M we get step-father(M, D).

Modus ponens on expression 2 with x = M, y = D, and z = F gives us father-in-law(M, F).

Finally using modus ponens on expression 3 with x = M, y = F, and z = M gives the result grandfather(M, M).

\item
\begin{enumerate}
\item
\{X/a,Z/Y\}
\item
No possible unification because two different ground instances cannot be substituted by the same variable.
\item
\{X/bill, Y/father(bill)\}
\item
This can't be unified because after substituting david for X the result is (father david), george). At this point we have two different constants and they cannot unified.   
\item
This cannot be unified because the first two terms are different constants. 
\end{enumerate}
\end{enumerate}
\end{document}